---
output: github_document
---

# unifyr

`unifyr` provides tools for auditing, validating, and preparing panel datasets before statistical analysis.

<!-- badges: start -->
[![R-CMD-check](https://github.com/desirajulavanya/R-Package-Unify/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/desirajulavanya/R-Package-Unify/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

## Installation

You can install the development version of `unifyr` from GitHub:

```{r eval=FALSE}
# install.packages("remotes")
remotes::install_github("desirajulavanya/R-Package-Unify")
```

## Why unifyr?

Panel datasets often contain missing unit-time cells, duplicate observations, irregular time gaps, and imbalance. These issues can affect fixed effects models, difference-in-differences designs, event studies, and other panel-data methods.

`unifyr` helps researchers identify and document these problems before estimation.

## Basic example

```{r}
library(unifyr)

data(example_panel)

example_panel
```

## Audit a panel dataset

```{r}
audit_panel(example_panel, id = id, time = year)
```

## Find duplicate unit-time observations

```{r}
duplicate_summary(example_panel, id = id, time = year)
```

## Summarize panel gaps

```{r}
gap_summary(example_panel, id = id, time = year)
```

## Flag row-level panel issues

```{r}
flag_panel_issues(example_panel, id = id, time = year)
```

## Complete the panel grid

`complete_panel()` creates a full unit-time grid while preserving observed values. It does not impute missing outcomes.

Because `complete_panel()` requires unique id-time cells, we first create a version of the example data without duplicates.

```{r}
example_panel_unique <- example_panel |>
  dplyr::distinct(id, year, .keep_all = TRUE)

complete_panel(example_panel_unique, id = id, time = year)
```

## Main functions

- `audit_panel()` gives a full panel diagnostic summary.
- `duplicate_summary()` finds duplicate unit-time observations.
- `gap_summary()` summarizes missing time periods by unit.
- `flag_panel_issues()` flags row-level panel problems.
- `complete_panel()` creates a complete panel grid without imputing observed variables.

## Package goal

The goal of `unifyr` is to provide a transparent and reproducible workflow for panel-data quality assurance before statistical modeling.
